\documentclass[11pt]{article}
\usepackage{hyperref}

\title{My \LaTeX\ Document}
\author{Teriz De Ocampo}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\pagebreak

  This will produce \textit{italicized} text.

  This will produce \textbf{bold-faced} text.

  This will produce \textsc{small caps} text.

  This will product \texttt{typewritter} text.

  Visit my portfolio at \url{http://theresa-de-ocampo.rf.gd/}.

  Visit my \href{http://theresa-de-ocampo.rf.gd/}{portfolio}.

  \vspace{1cm}

  Please excuse my \begin{large}dear aunt Sally.\end{large}

  Please excuse my \begin{Large}dear aunt Sally.\end{Large}

  Please excuse my \begin{LARGE}dear aunt Sally.\end{LARGE}

  Please excuse my \begin{huge} my dear aunt Sally.\end{huge}

  Please excuse my \begin{Huge} my dear aunt Sally.\end{Huge}

  \vspace{1cm}

  Please excuse my \begin{normalsize} my dear aunt Sally.\end{normalsize}

  Please excuse my \begin{small} my dear aunt Sally.\end{small}

  Please excuse my \begin{scriptsize} my dear aunt Sally.\end{scriptsize}

  Please excuse my \begin{tiny} my dear aunt Sally.\end{tiny}

  \vspace{1cm}

  \begin{center}
    This line is centered.
  \end{center}

  \begin{flushleft}
    This is left-aligned.
  \end{flushleft}

  \begin{flushright}
    This is right-aligned.
  \end{flushright}

  \section{Linear Functions}
    \subsection{Slope-Intercept Form}
      \subsubsection{Example 1}
      \subsubsection{Example 2}
    \subsection{Standard Form}
    \subsection{Point-Slope Form}
  \section{Quadratic Functions}
    \subsection{Vertex Form}
    \subsection{Standard Form}
    \subsection{Factored Form}

\end{document}